Deep Learning

### 2015-03-27 deepreview.tex
working on ref 2 comments

Learning which action will maximize the total future reward given a state
of the world is difficult when the rewards are delayed and the world has a
very large number of possible states. One impressive recent development is
a single system that can learn to play many different video
games~\citep{Deepmind-atari-arxiv2013}. The system uses a deep convolutional network to
map from the pixels on the screen at several time steps to the
expected future reward of each possible action (assuming some policy is followed
in the future) and its only inputs are the
pixels and the current score in the game. The learning works by minimizing
the difference between the system's current estimate of future reward and a
noisy but less biased estimate that is obtained by using the same deep
network to estimate the future reward of the next state, where the next
state is chosen stochastically based on the predicted future rewards of all
the currently legal actions.

@@

This review has focused on supervised learning because of its recent
achievements and we have ignored much interesting work on unsupervised
learning procedures for deep neural
networks~\citep{Salakhutdinov2009-small,Hinton95,QuocLe-ICML2012,VincentPLarochelleH2008-small,koray-nips-10,gregor-icml-10,ranzato-pami,Bengio-et-al-ICML-2014,Kingma-et-al-NIPS2014}.
However, most data have not been hand-labeled by humans, and just like
children are not told what they should have done at each instant, we
need learning machines that can learn from mostly unlabeled examples.
In the long run, we believe unsupervised learning will be essential
for allowing deep networks to generalize well by creating internal
representations that untangle the many different factors that interact
to produce images, speech and
documents~\citep{Bengio-Courville-Vincent-TPAMI2013}.

>>>>

Learning which action will maximize the total future reward given a state
of the world is difficult when the rewards are delayed and the world has a
very large number of possible states. After neural networks won backgammon
olympiads in the 90's~\citep{Tesauro90}, an impressive recent development is
combines deep convolutional networks with reinforcement learning in a single system that can learn to play many different video
games~\citep{Mnih-et-al-2015}. 
Pixels on the screen at several time steps are mapped to the
expected future reward of each possible action (assuming some policy is followed
in the future) and its only inputs are the
pixels and the current score in the game. The learning works by minimizing
the difference between the system's current estimate of future reward and a
noisy but less biased estimate that is obtained by using the same deep
network to estimate the future reward of the next state, where the next
state is chosen stochastically based on the predicted future rewards of all
the currently legal actions.

@@

This review has focused on supervised learning because of its recent
achievements and we have ignored much interesting work on unsupervised
learning procedures for deep neural
networks~\citep{Salakhutdinov2009-small,Hinton95,QuocLe-ICML2012,VincentPLarochelleH2008-small,koray-nips-10,gregor-icml-10,ranzato-pami,Bengio-et-al-ICML-2014,Kingma-et-al-NIPS2014}.
These papers often introduce a probabilistic view or the injection of randomness in the
neural network computation, to allow neural networks to {\em generate} examples that are
similar to training examples but generalize them.
Unsupervised learning is important because most data have not been hand-labeled by humans, and just like
children are not told what they should have done at each instant, we
need learning machines that can learn from mostly unlabeled examples.
In the long run, we believe unsupervised learning will be essential
for allowing deep networks to generalize well by creating internal
representations that untangle the many different factors that interact
to produce images, speech and
documents~\citep{Bengio-Courville-Vincent-TPAMI2013}.
